Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-03-29 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex Adding more comments...

\begin{lemma}\label{lemma:verify-convexity}
  To verify the convexity condition of a QIVPM
  $\mu : \events \rightarrow \mathscr{I}$, it is sufficient to check
  that:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{amr}
\end{equation}
 for all orthogonal projectors $P_{0}$ and~$P_{1}$.
\end{lemma}
\noindent The proof follows the outline of the proof of the classical
inclusion-exclusion principle. From the commuting projectors $P$ and
$P'$, we construct the following three orthogonal projectors: $PP'$,
$P(\mathbb{1}-P')$, and $(\mathbb{1}-P)P'$. Then we proceed as
follows:
\begin{widetext}
\begin{equation*}
\begin{aligned}
\noalign{$\bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right)$}
\qquad\qquad=~~&\bar{\mu}\left(PP'+P(\mathbb{1}-P')+P'-PP'\right)+\bar{\mu}\left(PP'\right) 
  & (\mbox{because } P = PP' + P - PP') \\
=~~& \bar{\mu}\left(P(\mathbb{1}-P')+P'\right)+\bar{\mu}\left(PP'\right) \\
=~~& \bar{\mu}\left(P(\mathbb{1}-P')+PP'+(\mathbb{1}-P)P'\right)+\bar{\mu}\left(PP'\right) 
      & (\mbox{because } P' = PP' + P' - PP') \\
=~~& \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
    \bar{\mu}\left(PP'\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\
=~~& \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') & (\mbox{using Eq.~(\ref{amr}) twice}) \\
=~~& \bar{\mu}(P) + \bar{\mu}(P')
\end{aligned}
\end{equation*}
\end{widetext}

@@

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove by contradiction that
$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
there is a state
$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
we assumed the core $\coreBorn\left(\bar{\mu},\events\right)$ 
is non-empty, so  $\muB_{\rho}(P)\in\bar{\mu}(P)$, and 
Table~\ref{tab:non-Born-QIVPM} tells us that
$\bar{\mu}(\proj{0})=\imposs=[0,0]$, we must conclude that
$\muB_{\rho}(\proj{0})=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
If this is true, then $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. {\color{red}Since any vector can be decomposed in terms of the
linearly independent basis $\left\{\ket{0},\ket{\ps},\ket{\ps'}\right\}$, all
$\ket{\phi_{j}}$ are perpendicular to any vector in the Hilbert space, and so
are not valid non-empty states, violating the assumption
$\ip{\phi_{j}}{\phi_{j}}=1$, and thus the theorem is proved.}

@@

\andy{no ending? What was the point of the section?}

>>>>

\begin{lemma}\label{lemma:verify-convexity}
  To verify the convexity condition of a QIVPM
  ${\color{red}\bar{\mu}} : \events \rightarrow \mathscr{I}$, it is sufficient to check
  that:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\label{amr}
\end{equation}
 for all orthogonal projectors $P_{0}$ and~$P_{1}$.
\end{lemma}
\noindent The proof follows the outline of the proof of the classical
inclusion-exclusion principle. From the commuting projectors $P$ and
$P'$, we construct the following three orthogonal projectors: $PP'$,
$P(\mathbb{1}-P')$, and $(\mathbb{1}-P)P'$. Then we proceed as
follows:
\begin{widetext}
\begin{equation*}
\begin{aligned}
\noalign{$\bar{\mu}\left(P+P'-PP'\right)+\bar{\mu}\left(PP'\right)$}
\qquad\qquad=~~&\bar{\mu}\left(PP'+P(\mathbb{1}-P')+P'-PP'\right)+\bar{\mu}\left(PP'\right) 
  & (\mbox{because } P = PP' + P - PP') \\
=~~& \bar{\mu}\left(P(\mathbb{1}-P')+P'\right)+\bar{\mu}\left(PP'\right) \\
=~~& \bar{\mu}\left(P(\mathbb{1}-P')+PP'+(\mathbb{1}-P)P'\right)+\bar{\mu}\left(PP'\right) 
      & (\mbox{because } P' = PP' + P' - PP') \\
=~~& \bar{\mu}(P(\mathbb{1}-P'))+\bar{\mu}(PP')+\bar{\mu}((\mathbb{1}-P)P')+
    \bar{\mu}\left(PP'\right) & (\mbox{using Eq.~(\ref{amr}) twice}) \\
=~~& \bar{\mu}(P(\mathbb{1}-P')+PP')+\bar{\mu}((\mathbb{1}-P)P'+PP') & (\mbox{using Eq.~(\ref{amr}) twice}) \\
=~~& \bar{\mu}(P) + \bar{\mu}(P')
\end{aligned}
\end{equation*}
\end{widetext}

@@

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, 
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove by contradiction that
$\coreBorn\left(\bar{\mu},\events\right)$ is the empty set. Suppose
there is a state
$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j} > 0$. Since
we assumed the core $\coreBorn\left(\bar{\mu},\events\right)$ 
is non-empty, so  $\muB_{\rho}(P)\in\bar{\mu}(P)$, and 
Table~\ref{tab:non-Born-QIVPM} tells us that
$\bar{\mu}(\proj{0})=\imposs=[0,0]$, we must conclude that
$\muB_{\rho}(\proj{0})=0\in[0,0]$, and similarly for $\proj{\ps}$ and $\proj{\ps'}$.
If this is true, then $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all~$j$. {\color{red}Since any vector can be decomposed in terms of the
linearly independent basis $\left\{\ket{0},\ket{\ps},\ket{\ps'}\right\}$, all
$\ket{\phi_{j}}$ are perpendicular to any vector in the Hilbert space, and so
are not valid non-empty states, violating the assumption
$\ip{\phi_{j}}{\phi_{j}}=1$, and thus the theorem is proved.}
\yutsung{The new text seems not very smooth. How about the following?}
If this is true, then $\ip{0}{\phi_{j}}=\ip{\ps}{\phi_{j}}=\ip{\ps'}{\phi_{j}}=0$
for all~$j$. This follows that
\begin{subequations}
\begin{eqnarray}
 &  & \ip{1}{\phi_{j}}=\sqrt{2}\ip{\ps}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,,\\
 &  & \ip{2}{\phi_{j}}=\sqrt{2}\ip{\ps'}{\phi_{j}}-\ip{0}{\phi_{j}}=0\,,
\end{eqnarray}
\end{subequations}
so
that$\ket{\phi_{j}}=\ket{0}\ip{0}{\phi_{j}}+\ket{1}\ip{1}{\phi_{j}}+\ket{2}\ip{2}{\phi_{j}}=0$.
This violates the fact that $\ket{\phi_{j}}$ is a normalized state, and thus the
theorem is proved.
\yutsung{End of the suggested text.}

@@

\andy{no ending? What was the point of the section?}
\yutsung{Begin of comments}
Can this relate it to the following theorem:
\begin{thm}Any ($\rho \rightarrow \rho$)-computable function~$f$ mapping between
continuums, like unit interval $[0,1]$, is continuous
\cite{Ziegler2007,weihrauch2012computable}.\end{thm}
The idea is that when we mapping between continuums, only continuous functions
could be approximated, and discontinuous functions might be too wild to be approximated...
However, I don't know how to fit this idea with other part of the paper...
\yutsung{End of comments}
